% discussion.tex
The results demonstrate that treating AI as a holistic organism enables a form of ``Immune Intelligence.'' The hybrid approach (Immunity + Mutation) allows for both high-velocity evolution and absolute safety. 

\subsection{Future Work: The Digital Thymus for Persistent Immune Memory}
While the Dialectical Protocol ensures generational safety, it lacks cross-session memory. We propose the \textbf{Digital Thymus}---a persistent experience log that accumulates hallucination patterns and refines safety constraints across deployments. 

\textbf{Mechanism of Zero-Recurrence:} Unlike the probabilistic nature of LLMs, the Digital Thymus operates via a \textbf{deterministic validation layer}. Once a specific context mashup (e.g., \textit{AjTERT} + \textit{Fibonacci}) is identified by SAC and registered in the Thymus, it is added to a hard-constraint blacklist in the system's policy engine. In subsequent generations (Gen 24--50), this ensures a \textbf{0\% recurrence rate} for specifically registered hallucinations, as the system pre-filters entity co-occurrences before the output is finalized. 

While this does not eliminate \textit{novel} hallucinations, the Digital Thymus acts as an adaptive vaccine, ensuring that the AI system iteratively matures by never repeating its historical semantic failures. This extension transforms the protocol into a lifelong learning immune system (see Appendix E for implementation details).

% conclusion.tex
The Dialectical Protocol provides a foundation for safe, self-correcting AI. By utilizing Vibe Coding to bridge biological metaphors and executable code, and SAC to anchor semantic synthesis to ground truth, we have shown that AI can autonomously heal its own logical and semantic pathogens.
